### 2023-11-29 manuscript.tex
Updated working title
Added TODO for abstract
Added conserved figure

\textbf{Title:} Evolutionary analyses of IDRs reveal patterns of conserved features

@@

@@

>>>>

\textbf{Title:} Evolutionary analyses of IDRs reveal widespread signals of conservation

@@

% TODO: Re-write last few sentences of abstract to reflect weakened conclusion

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{conserved/out/conserved.png}
\centering
\caption{\textbf{Distributions of significant features in regions.}
\textbf{(A)} Fraction of regions with significant likelihood ratios for each feature under 1 and 5\% type I error rates. \textbf{(B)} Distribution of number of features with significant likelihood ratios under 1 (left) and 5\% type I error rates. The random distributions were computed by randomly shuffling the observed likelihood ratios between regions for each feature independently.}
\label{fig:conserved}
\end{figure}
